The SMT Competition 2015--2018

### 2019-04-11 2018/report/SMT-COMP.tex
adding further analysis tables still need to add text

@@

\subsection{Further Analysis}

@@

\paragraph{Progress in solver performance.}

@@

\paragraph{Unique solutions.}

@@

\paragraph{Use of parallelism.}

@@

>>>>

It is interesting to note that the non-competitive solvers MathSAT and Z3 often appear as the best performing solver. We do not see this as detracting from the overall significance of results. Both solvers are industrial-strength tools, actively maintained and tuned. The reasons for non-entry into the competition are orthogonal to their suitability for the competition. Indeed, Z3 has been entered into the competition competitively in the past and one can assume was trained on the current problems (as much as any solver is). Finally, the fact that industrial-strength solvers perform well in the competition supports the notion that the benchmarks in the competition are industrially relevant.

@@

\section{Further Analysis}

@@

\subsection{Progress in Solver Performance.}

@@

\subsection{Unique Solutions.}

@@

\subsection{Use of Parallelism.}

@@

\subsection{Focussing on Satisfiability or Unsatisfiability}

In the Main-track all divisions contain a mixture of problems that are satisfiable and unsatisfiable. However, some solvers may be specialised or optimised for a particular kind of problem. Therefore, it is interesting to ask whether the winners of divisions might have changed if benchmarks in that division had been restricted to one of these results. Table~\ref{tab:results:sat:unsat} shows the changes in division winners if only satisfiable or unsatisfiable results are given.

\begin{table}
\caption{Alternative winners if only Satisfiable (top) or Unsatisfiable (bottom) benchmarks had been considered. These results are in reference to those given in Table~\ref{tab:winners-main}.\label{tab:results:sat:unsat}}
\centering
\begin{tabular}{r@{\hskip 1em}>{\columncolor[gray]{.95}[.25em][.5em]}c@{\hskip 1em}>{\columncolor[gray]{.95}[.5em][.5em]}c@{\hskip 1em}>{\columncolor[gray]{.95}[.5em][.5em]}c@{\hskip 1em}>{\columncolor[gray]{.95}[.5em][0.25em]}c}
\toprule
Division         &  2015                 &  2016                    &  2017                  &  2018                      \\
\hline \hline
AUFLIA  & CVC3  &   &   & Alt-Ergo  \\
AUFNIRA & \nc{Z3}  & CVC4 \nc{Z3}  & CVC4 \nc{Z3}  & \nc{Z3}  \\
NIA     & CVC3  &   &   &   \\
NRA     & CVC3  & CVC4  & CVC4  & CVC4\nc{Z3}Z3  \\
QF\_AUFBV        & Yices  & Yices2  &   & Yices2  \\
QF\_LIA  & \nc{Z3}  &   &   &   \\
QF\_UFIDL        & \nc{Z3}  & \nc{Z3}  & \nc{Z3}  & \nc{Z3} veriT  \\
QF\_UFNIA        & CVC3  &   & CVC4  &   \\
UFLIA   & \nc{Z3}  &   &   &   \\
UFLRA   & CVC3  & CVC4  &   &   \\
AUFLIRA &   & CVC4  & CVC4  & Alt-Ergo  \\
BV      &   & \nc{Z3}  & Boolector  & Boolector  \\
QF\_ABV  &   & Yices2  & Yices2  &   \\
QF\_BV   &   & MinkeyRink  &   &   \\
QF\_NIA  &   & SMT-RAT  &   &   \\
UF      &   & Vampire  &   &   \\
UFBV    &   & Boolector  &   &   \\
UFNIA   &   & CVC4  & CVC4  & CVC4  \\
LRA     &   &   & veriT+Redlog  &   \\
QF\_LRA  &   &   & Yices2  & Yices2  \\
QF\_NIRA &   &   & CVC4  &   \\
QF\_NRA  &   &   & \nc{Z3}  &   \\
UFDTLIA &   &   & CVC4  &   \\
ALIA    &   &   &   & Alt-Ergo  \\
QF\_FP   &   &   &   & CVC4  \\
QF\_UFBV &   &   &   & Yices2  \\
\bottomrule
\end{tabular}

\begin{tabular}{r@{\hskip 1em}>{\columncolor[gray]{.95}[.25em][.5em]}c@{\hskip 1em}>{\columncolor[gray]{.95}[.5em][.5em]}c@{\hskip 1em}>{\columncolor[gray]{.95}[.5em][.5em]}c@{\hskip 1em}>{\columncolor[gray]{.95}[.5em][0.25em]}c}
\toprule
Division         &  2015                 &  2016                    &  2017                  &  2018                      \\
\hline \hline
QF\_AUFNIA       & \nc{Z3}  & \nc{Z3}  &   &   \\
QF\_IDL  & CVC4  &   & \nc{Z3}  & CVC4 \nc{Z3}  \\
QF\_LIA  & SMTInterpol  & SMTInterpol  & SMTInterpol  & SMTInterpol  \\
QF\_NIA  & CVC3  &   & Yices2  &   \\
BV      &   & CVC4  &   &   \\
NIA     &   & CVC4  & Vampire  & Vampire  \\
QF\_UFNRA        &   & CVC4 \nc{Z3}  & CVC4  & CVC4 \nc{Z3}  \\
UFIDL   &   & Vampire \nc{Z3}  & \nc{Z3}  &   \\
QF\_AUFBV        &   &   & CVC4  &   \\
QF\_BV   &   &   & Boolector  &   \\
QF\_UFLIA        &   &   & \nc{Z3}  &   \\
UF      &   &   & CVC4  & CVC4  \\
UFLRA   &   &   & veriT  & veriT  \\
QF\_NRA  &   &   &   & CVC4  \\
\bottomrule
\end{tabular}

\end{table}

\subsection{Very Quick Solutions}

Table~\ref{tab:results:24s}

\begin{table}
\caption{Alternative winners if the time limit had been 24 seconds.\label{tab:results:24s}}
\centering

\begin{tabular}{r@{\hskip 1em}>{\columncolor[gray]{.95}[.25em][.5em]}c@{\hskip 1em}>{\columncolor[gray]{.95}[.5em][.5em]}c@{\hskip 1em}>{\columncolor[gray]{.95}[.5em][.5em]}c@{\hskip 1em}>{\columncolor[gray]{.95}[.5em][0.25em]}c}
\toprule
Division         &  2015                 &  2016                    &  2017                  &  2018                      \\
\hline \hline
AUFLIRA & CVC3  &   &   & Alt-Ergo  \\
AUFNIRA & \nc{Z3}  &   &   & \nc{Z3}  \\
QF\_BV   & CVC4  & STP \nc{Z3}  &   & Boolector  \\
QF\_LIA  & Yices  & Yices2  & Yices2  &   \\
QF\_LRA  & Yices  & Yices2  & Yices2  & Yices2  \\
QF\_UF   & veriT  & veriT  &   &   \\
UFNIA   & \nc{Z3}  &   &   & \nc{Z3}  \\
AUFLIA  &   & Vampire \nc{Z3}  & veriT  &   \\
QF\_ABV  &   & Yices2  &   &   \\
QF\_ANIA &   & \nc{Z3}  & \nc{Z3}  &   \\
QF\_UFNRA        &   & CVC4 \nc{Z3}  & CVC4  & \nc{Z3}  \\
UF      &   & Vampire  &   &   \\
UFBV    &   & Boolector  &   &   \\
UFIDL   &   & Vampire \nc{Z3}  & \nc{Z3}  &   \\
QF\_NIA  &   &   & Yices2  & Yices2  \\
QF\_NIRA &   &   & Yices2 Z3  & Yices2 \nc{Z3}  \\
QF\_NRA  &   &   & \nc{Z3}  &   \\
UFLRA   &   &   & veriT  & veriT  \\
BV      &   &   &   & Boolector \nc{Z3}  \\
NRA     &   &   &   & CVC4 \nc{Z3}  \\
UFLIA   &   &   &   & \nc{Z3}  \\
\bottomrule
\end{tabular}
\end{table}

\subsection{Do Families Matter?}

Table~\ref{tab:results:total:solved}

\begin{table}
\caption{Alternative winners if families were not used in computing scores e.g. the 2015 scoring system were used.\label{tab:results:total:solved}}
\centering
\begin{tabular}{r@{\hskip 1em}>{\columncolor[gray]{.95}[.25em][.5em]}c@{\hskip 1em}>{\columncolor[gray]{.95}[.5em][.5em]}c@{\hskip 1em}>{\columncolor[gray]{.95}[.5em][.5em]}c@{\hskip 1em}>{\columncolor[gray]{.95}[.5em][0.25em]}c}
\toprule
Division         &  2015                 &  2016                    &  2017                  &  2018                      \\
\hline\hline
AUFNIRA &   & CVC4  &   &   \\
UFIDL   &   & \nc{Z3}  &   &   \\
BV      &   &   & Boolector  &   \\
QF\_LRA  &   &   & Yices2  & SPASS-SATT  \\
QF\_NIA  &   &   & Yices2  & Yices2  \\
QF\_BV   &   &   &   & Boolector  \\
QF\_FP   &   &   &   & CVC4  \\
\bottomrule
\end{tabular}
\end{table}
